### 2017-05-11 paper/utilityFunctions.tex
replaced png pictures with pdf ones

\section{Utility Functions}\label{utilfns}
To be able to go into detail on parallel arrows, we introduce some utility combinators first, that will help us later: \lstinline{map}, \lstinline{foldl} and \lstinline{zipWith} on Arrows.\olcomment{capitalisation! arrows vs. Arrows!}

>>>>

\section{Utility Functions}\label{utilfns}
To be able to go into detail on parallel arrows, we introduce some utility combinators first, that will help us later: \lstinline{map}, \lstinline{foldl} and \lstinline{zipWith} on arrows.
